Cell Decomposition of Rank 2 Quiver Grassmannians

### 2017-08-12 Grassmannian_cells.tex
Added results relating to piecewise compatibility.  Corollary 6.10 gives the combinatorial description of the 'empty fibers'.

\begin{lemma}
  For any $m\ge1$, we have 
  \[\dim\Hom(P_m,P_m)=1,\quad \dim\Hom(P_m,P_{m+1})=n,\quad \dim\Hom(P_{m+1},P_m)=0, \quad\dim\Ext(P_{m+1},P_m)=0.\]  
  Moreover, for $1\le k<n$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$ is injective. 
\end{lemma}
\begin{proof} 
  Note that we have an Auslander-Reiten sequence
  \begin{equation}
  \label{eq:AR sequence}
    0\longrightarrow P_{m-1}\longrightarrow P_m^n\stackrel{[f_1\ \cdots\ f_n]}{\longrightarrow} P_{m+1}\longrightarrow 0
  \end{equation}
  with irreducible homomorphisms $f_i$ which are also linearly independent. 
  Thus they do not factor through a representation $Z\neq P_{m}$ which already means that they are injective, see for instance \cite[Lemma 1.6]{ass}. 
  If we pick $k<n$ linear independent homomorphisms $f_{i_1},\ldots, f_{i_k}$, this also means that $[f_{i_1}\ \cdots\ f_{i_k}]:P_m^k\to P_{m+1}$ is injective. 
  Indeed otherwise, at least one of the homomorphisms were forced to factor through a representation $Z\neq P_{m}$.
\end{proof}

@@

  To see (2), we apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get an isomorphism $\Hom(P_m^k,P_m)\cong\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$.
  Observe that $\Hom(P_m^k,P_m)$ is spanned by the coordinate projections $\pi_i:P_m^k\to P_m$ for $1\le i\le k$ and each of these gives rise to a commutative diagram
  \[\xymatrix{ & 0\ar[d] & 0\ar[d] & & \\ & P_m^{k-1}\ar[d]\ar@{=}[r]& P_m^{k-1}\ar[d]^{[f_1\ \cdots\ \widehat{f_i}\ \cdots\ f_k]}& & \\
    0\ar[r]& P_m^k\ar[r]^{[f_1\ \cdots\ f_k]}\ar[d]^{\pi_i}\ar@{}[dr]|(.35){\ulcorner}& P_{m+1}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar@{=}[d]& 0 \\
    0\ar[r]& P_m\ar[r]^(.35){f_i}\ar[d]& P_{m+1}^{\{f_1,\ldots,\widehat{f_i},\ldots,f_k\}}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]& 0\\
     & 0 & 0 & & }\]
  where $\hat f_k$ above indicates that the function $f_k$ has been omitted.
  The bottom row of this diagram is the extension in $\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$ which can be naturally identified with the generator $f_i$ of $\kk f_1\oplus\cdots\oplus\kk f_k$.

@@

\begin{lemma}
  Let $f_1,\ldots,f_n\in\Hom(P_m,P_{m+1})$ be linearly independent morphisms and write $g:P_{m-1}\to P_m$ for the composition of the inclusion from \eqref{eq:AR sequence} with the projection $\pi_n:P_m^n\to P_m$ to the $n^{th}$ factor.  Then $P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}\cong P_m^{\{g\}}$.
\end{lemma}
\begin{proof}
  We have the following commutative diagram
  \[\xymatrix{0\ar[r]& P_m^{n-1}\ar@{=}[d]\ar[r]& P_m^n\ar[r]^{\pi_n}\ar[d]^{[f_1\ \cdots\ f_n]}\ar@{}[dr]|(.65){\lrcorner}& P_m\ar[r]\ar[d]^{f_n}& 0 \\
  0\ar[r]& P_m^{n-1}\ \ \ \ar[r]^{[f_1\ \cdots\ f_{n-1}]}&\ \ \ P_{m+1}\ar[r]& P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}\ar[r]& 0}\]
  Since the vertical morphism on the left is an equality, the right hand square is a pullback.  
  But this implies the kernels of the vertical morphisms coincide.  
  The middle vertical morphism fits into the exact sequence \eqref{eq:AR sequence} and so the kernel is $P_{m-1}$.
  It follows that the resulting morphism $g:P_{m-1}\to P_m$, which is the kernel of the right-hand vertical morphism, satisfies $P_m^{\{g\}}\cong P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}$.
\end{proof}

For any nonempty subset $I\subset[1,k]$, say with $|I|=\ell$, we get an exact sequence
\[0\longrightarrow P_m^\ell\stackrel{[f_i]_{i\in I}}{\longrightarrow} P_{m+1}^{\{f_j\}_{j\in[1,k]\setminus I}}\longrightarrow P_{m+1}^{\{f_1,\ldots,f_k\}}\longrightarrow 0.\]
Each such sequence has the following almost-split property for subrepresentations of $P_{m+1}^{\{f_1,\ldots,f_k\}}$.
\begin{lemma}
  For $m\ge1$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, given any proper subrepresentation $V\subsetneq P_{m+1}^{\{f_1,\ldots,f_k\}}$, the upper pullback sequence
  \[\xymatrix{0\ar[r] & P_m^\ell\ar@{=}[d]\ar[r] & V^I\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & V\ar[d]\ar[r] & 0 \\
  0\ar[r]& P_m^\ell\ar[r]^(.35){[f_i]_{i\in I}} & P_{m+1}^{\{f_j\}_{j\in[1,k]\setminus I}}\ar[r]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]& 0}\]
  splits for every $I\subset[1,k]$.
\end{lemma}
\begin{proof}
  When $I=\emptyset$, we have $\ell=0$ and there is nothing to show, so assume $I$ is a nontrivial subset of $[1,k]$.

@@

For $m\ge2$ and $1\le r\le n-1$, write $D_m^{(r)}$ for the maximal Dyck path obtained from $D_m$ by removing the first $r$ copies of $D_{m-1}$.
Note that by Theorem~\ref{th:dyck path recursion}, we have a natural identification of $D_m^{(n-1)}$, $m\ge3$, with $D_{m-1}^{(1)}$.
For fixed $m\ge2$ and $1\le r\le n-1$, we write $D_{m-1,r}$ for the $r$-th copy of $D_{m-1}$ inside $D_m$.
For notational convenience we also set $D_{m-1,n}:=D_m^{(n-1)}$  even though this maximal Dyck path does not identify with a copy of $D_{m-1}$.

@@

Given edges $e,e'\in E_m$ with $e<e'$, write $ee'$ for the shortest subpath of $D_m$ containing $e$ and $e'$, in particular $ee$ is the subpath containing the single edge $e$.
\begin{definition}
  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{compatible} if: 
  for each pair $(h,v)\in S_H\times S_V$ with $h<v$ there exists an edge $e\in hv$ so that at least one of the following holds
  \begin{equation}
    \label{eq:hgc}
    e\ne v\qquad\text{and}\qquad |he\cap S_V|=n|he\cap S_H|
  \end{equation}
  or
  \begin{equation}
    \label{eq:vgc}
    e\ne h\qquad\text{and}\qquad |ev\cap S_H|=n|ev\cap S_V|.
  \end{equation}
  Write $\cC_m$ for the collection of all pairs $(S_H,S_V)$ which are compatible as above.
\end{definition}
\begin{remark}
  This notion of compatibility extends naturally to the maximal Dyck paths $D_m^{(r)}$, $1\le r\le n-1$.  Write $\cC_m^{(r)}$ for the set of all compatible pairs in $D_m^{(r)}$.
\end{remark}

The recursive structure of the maximal Dyck paths from Theorem~\ref{th:dyck path recursion} gives rise to a recursive characterization of compatible pairs.
\begin{definition}
  \cite[Definition 3.11]{rupel}
  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{piecewise compatible} if one of the conditions \eqref{eq:hgc} or \eqref{eq:vgc} is satisfied for each pair $(h,v)\in(S_H\cap H_{m-1,r})\times(S_V\cap V_{m-1,r})$ $h\in H_{m-1,r}$ and $v\in V_{m-1,r}$ for some $1\le r\le n-1$.
\end{definition}

@@

Our goal is to show that the compatible pairs provide a natural labelling for the cells of $\chi\big(Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.

@@

\bibitem{rupel} Rupel, D.: Rank 2 Non-Commutative Laurent Phenomenon and Pseudo-Positivity, arXiv.

>>>>

\begin{lemma}
  For any $m\ge1$, we have 
  \[\dim\Hom(P_m,P_m)=1,\quad \dim\Hom(P_m,P_{m+1})=n,\quad \dim\Hom(P_{m+1},P_m)=0, \quad\dim\Ext(P_{m+1},P_m)=0.\]  
  Moreover, for $1\le k<n$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$ is injective. 
\end{lemma}
\begin{proof} 
  Note that we have an Auslander-Reiten sequence
  \begin{equation}
    \label{eq:AR sequence}
    0\longrightarrow P_{m-1}\stackrel{\iota}{\longrightarrow} P_m^n\stackrel{[f_1\ \cdots\ f_n]}{\longrightarrow} P_{m+1}\longrightarrow 0
  \end{equation}
  with irreducible homomorphisms $f_i$ which are also linearly independent. 
  Thus they do not factor through a representation $Z\neq P_{m}$ which already means that they are injective, see for instance \cite[Lemma 1.6]{ass}. 
  If we pick $k<n$ linearly independent homomorphisms $f_{i_1},\ldots, f_{i_k}$, this also means that $[f_{i_1}\ \cdots\ f_{i_k}]:P_m^k\to P_{m+1}$ is injective. 
  Indeed otherwise, at least one of the homomorphisms would be forced to factor through a representation $Z\neq P_{m}$.
\end{proof}

@@

  To see (2), we apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get an isomorphism $\Hom(P_m^k,P_m)\cong\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$.
  Observe that $\Hom(P_m^k,P_m)$ is spanned by the coordinate projections $\pi_i:P_m^k\to P_m$ for $1\le i\le k$ and each of these gives rise to a commutative diagram
  \[\xymatrix{ & 0\ar[d] & 0\ar[d] & & \\ & P_m^{k-1}\ar[d]\ar@{=}[r]& P_m^{k-1}\ar[d]^{[f_1\ \cdots\ \widehat{f_i}\ \cdots\ f_k]}& & \\
    0\ar[r]& P_m^k\ar[r]^{[f_1\ \cdots\ f_k]}\ar[d]^{\pi_i}\ar@{}[dr]|(.35){\ulcorner}& P_{m+1}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar@{=}[d]& 0 \\
    0\ar[r]& P_m\ar[r]^(.35){f_i}\ar[d]& P_{m+1}^{\{f_1,\ldots,\widehat{f_i},\ldots,f_k\}}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]& 0\\
     & 0 & 0 & & }\]
  where $\hat f_i$ above indicates that the function $f_i$ has been omitted.
  The bottom row of this diagram is the extension from $\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$ which is naturally identified with the generator $f_i$ of $\kk f_1\oplus\cdots\oplus\kk f_k$.

@@

\begin{lemma}
  Let $f_1,\ldots,f_n\in\Hom(P_m,P_{m+1})$ be linearly independent morphisms and write $g:P_{m-1}\to P_m$ for the composition of the inclusion $\iota:P_{m-1}\hookrightarrow P_m^n$ from \eqref{eq:AR sequence} with the projection $\pi_n:P_m^n\to P_m$ to the $n$-th factor.  Then $P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}=P_m^{\{g\}}$.
\end{lemma}
\begin{proof}
  We have the following commutative diagram
  \[\xymatrix{0\ar[r]& P_m^{n-1}\ar@{=}[d]\ar[r]& P_m^n\ar[r]^{\pi_n}\ar[d]^{[f_1\ \cdots\ f_n]}\ar@{}[dr]|(.65){\lrcorner}& P_m\ar[r]\ar[d]^{f_n}& 0 \\
  0\ar[r]& P_m^{n-1}\ \ \ \ar[r]^{[f_1\ \cdots\ f_{n-1}]}&\ \ \ P_{m+1}\ar[r]& P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}\ar[r]& 0}\]
  Since the vertical morphism on the left is an equality, the right hand square is a pullback.  
  But this implies the kernels of the vertical morphisms coincide.

  The middle vertical morphism fits into the exact sequence \eqref{eq:AR sequence} and so its kernel is $P_{m-1}$.
  It follows that the resulting morphism $g:P_{m-1}\to P_m$, which is the kernel of the right-hand vertical morphism, satisfies $P_m^{\{g\}}=P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}$.
\end{proof}

For any nonempty subset $I\subset[1,k]$, say with $|I|=\ell$, we get an exact sequence
\[0\longrightarrow P_m^\ell\stackrel{[f_i]_{i\in I}}{\longrightarrow} P_{m+1}^{\{f_j\}_{j\in[1,k]\setminus I}}\longrightarrow P_{m+1}^{\{f_1,\ldots,f_k\}}\longrightarrow 0.\]
Each such sequence has the following almost-split property for subrepresentations of $P_{m+1}^{\{f_1,\ldots,f_k\}}$.
\begin{lemma}
  For $m\ge1$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, given any proper subrepresentation $V\subsetneq P_{m+1}^{\{f_1,\ldots,f_k\}}$, the upper pullback sequence
  \[\xymatrix{0\ar[r] & P_m^\ell\ar@{=}[d]\ar[r] & V^I\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & V\ar[d]\ar[r] & 0 \\
  0\ar[r]& P_m^\ell\ar[r]^(.35){[f_i]_{i\in I}} & P_{m+1}^{\{f_j\}_{j\in[1,k]\setminus I}}\ar[r]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]& 0}\]
  splits for every $I\subset[1,k]$.
\end{lemma}
\begin{proof}
  When $I=\varnothing$, we have $\ell=0$ and there is nothing to show, so assume $I$ is a nontrivial subset of $[1,k]$.

@@

We obtain the following as an immediate consequence.
\begin{corollary}
  \label{cor:short hooks}
  Inside $D_m$, $m\ge2$, there are precisely $u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges.
\end{corollary}
\begin{proof}
  We work by induction on $m\ge2$.
  The cases $m=2,3$ are immediate from Theorem~\ref{th:dyck path recursion} parts (2) and (3).
  For $m\ge4$, part (3) of Theorem~\ref{th:dyck path recursion} shows by induction that there are $(n-1)u_{m-3}+(u_{m-3}-u_{m-4})=u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges.
\end{proof}

For $m\ge2$ and $1\le k\le n-1$, write $D_m^{(k)}$ for the maximal Dyck path obtained from $D_m$ by removing the first $k$ copies of $D_{m-1}$.
Extending this notation we also set $D_m^{(0)}:=D_m$.
\begin{remark}
  Note that by Theorem~\ref{th:dyck path recursion}, we have a natural identification of $D_m^{(n-1)}$, $m\ge3$, with $D_{m-1}^{(1)}$.
\end{remark}
For fixed $m\ge2$ and $1\le r\le n-1$, we write $D_{m-1,r}$ for the $r$-th copy of $D_{m-1}$ inside $D_m$.
For notational convenience we also set $D_{m-1,n}:=D_m^{(n-1)}$ even though this maximal Dyck path does not identify with a copy of $D_{m-1}$.
For $m\ge2$ and $1\le k\le n-1$, the maximal Dyck paths $D_{m-1,r}$, $k+1\le r\le n$, naturally identify with subpaths of $D_m^{(k)}$.

@@

Given edges $e,e'\in E_m$ with $e<e'$, write $ee'$ for the shortest subpath of $D_m$ containing $e$ and $e'$, in particular $ee$ is the subpath containing the single edge $e$.
\begin{definition}
  \label{def:compatibility}
  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{compatible} if: 
  for each pair $(h,v)\in S_H\times S_V$ with $h<v$ there exists an edge $e\in hv$ so that at least one of the following holds
  \begin{equation}
    \label{eq:hgc}
    e\ne v\qquad\text{and}\qquad |he\cap V_m|=n|he\cap S_H|
  \end{equation}
  or
  \begin{equation}
    \label{eq:vgc}
    e\ne h\qquad\text{and}\qquad |ev\cap H_m|=n|ev\cap S_V|.
  \end{equation}
  Write $\cC_m$ for the collection of all pairs $(S_H,S_V)$ which are compatible as above.
\end{definition}
\begin{remark}
  This notion of compatibility extends naturally to the maximal Dyck paths $D_m^{(k)}$, $1\le k\le n-1$.  Write $\cC_m^{(k)}$ for the set of all compatible pairs in $D_m^{(k)}$.
\end{remark}

The recursive structure of the maximal Dyck paths from Theorem~\ref{th:dyck path recursion} gives rise to a recursive characterization of compatible pairs.
\begin{definition}
  \cite[Definition 3.11]{rupel}
  \label{def:piecewise compatibility}
  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{piecewise compatible} if, for each $1\le r\le n$, one of the conditions \eqref{eq:hgc} or \eqref{eq:vgc} is satisfied for each pair $(h,v)\in S_H\times S_V$ with $h\in H_{m-1,r}$ and $v\in V_{m-1,r}$.
\end{definition}
\begin{remark}
  The notion of piecewise compatibility naturally extends to the maximal Dyck paths $D_m^{(k)}$, $1\le k\le n-1$.
\end{remark}

To describe precisely when a piecewise compatible pair $(S_H,S_V)$ is compatible we need more notation.
For a horizontal edge $h\in H_m$ and a subset $S_H\subset H_m$, write $D(h;S_H)=he$ for the shortest subpath of $D_m$ for which $|he\cap V_m|=n|he\cap S_H|$, if no such subpath exists we set $D(h;S_H)=hv_{u_{m-1}}$.
The subpath $D(h;S_H)$ is called the \emph{local shadow path} of $h$ with respect to $S_H$.
Similarly, for a vertical edge $v\in V_m$ and a subset $S_V\subset V_m$, the \emph{local shadow path} of $v$ with repect to $S_V$ is $D(v;S_V)=ev$ for the shortest subpath of $D_m$ for which $|ev\cap H_m|=n|ev\cap S_V|$ and we take $D(v;S_V)=h_1v$ if there does not exist such an edge $e$.
\begin{definition}
  \cite[Definition 3.17]{rupel}
  A horizontal edge $h_i\in H_m$, $m\ge3$, is called \emph{blocking} for a subset $S_H\subset H_m$ if $D(h_i;S_H)=h_iv_{u_{m-1}}$ and $h_i$ is furthest to the right with this property, i.e.\ the index $i$ is maximal with this property.

  Suppose $S_H\subset H_m$ admits a blocking edge $h_i\in H_m$.
  Then $S_H$ is \emph{left-justified at $h_i$} if there exists $k\ge i$ so that $S_H=\{h_i,h_{i+1},\ldots,h_k\}$.
  The subset $S_H$ is \emph{strongly left-justified at $h_i$} if $S_H$ is left-justified at $h_i$ and $|h_iv_{u_{m-1}}\cap V_m|=n|h_iv_{u_{m-1}}\cap S_H|$.

  A subset $S_V\subset V_m$ is \emph{right-justified with respect to $h_i$} if there exists a vertical edge $v_s\in h_iv_{u_{m-1}}$ so that $S_V\cap h_iv_{u_{m-1}}=\{v_s,v_{s-1},\ldots,v_{u_{m-1}}\}$.
  The subset $S_V$ is \emph{strongly right-justified with respect to $h_i$} if $S_V$ is right-justified with respect to $h_i$ and $D(v_{u_{m-1}};S_V)=h_iv_{u_{m-1}}$ with $|h_iv_{u_{m-1}}\cap H_m|=n|h_iv_{u_{m-1}}\cap S_V|$.
\end{definition}

\begin{theorem}
  \cite[Theorem 3.20 and Corollary 3.22]{rupel}
  \label{th:blocking edge conditions}
  For $m\ge3$, suppose $S_H\subset H_m$ and $S_V\subset V_m$ are piecewise compatible. 
  Then the following hold:
  \begin{enumerate}
    \item If $S_H$ does not admit a blocking edge, then $(S_H,S_V)\in\cC_m$.
    \item Suppose $S_H$ admits a blocking edge $h_i\in H_m$ and $(S_H,S_V)$ is not compatible.
      Then $S_H$ is left-justified at $h_i$ and $S_V$ is strongly right-justified with respect to $h_i$.
      In addition the following hold:
      \begin{enumerate}
        \item If $m=3$, then $S_H\cap h_iv_{u_{m-1}}=\{h_i\}$.
        \item If $m\ge4$, then $S_H$ is strongly left-justified at $h_i$.
        \item If $m\ge5$, then either $i=1$ or $h_i$ is immediately preceded by a vertical edge in $D_m$.
      \end{enumerate}
  \end{enumerate}
\end{theorem}

\begin{corollary}
  For $m\ge4$ and $0\le k\le n-1$, consider $S_H\subset H_m^{(k)}$ and $S_V\subset V_m^{(k)}$ so that $(S_H,S_V)$ is piecewise compatible.
  Assume $\big(S_H^{(k+1)},S_V^{(k+1)}\big)\in\cC_m^{(k+1)}$.
  Then $(S_H,S_V)$ is not compatible if and only if $H_{m-2}^{(k+1)}\subset S_{H,k+1}$ and $V_m^{(k+1)}\subset S_V$.
\end{corollary}
\begin{proof}
  We begin with the reverse implication.
  First note that there are $(n-k)u_{m-1}-u_{m-2}$ horizontal edges and $(n-k)u_{m-2}-u_{m-3}$ vertical edges in $D_m^{(k)}$. 
  It follows that $V_{m-2}^{(k+1)}\sqcup V_m^{(k+1)}$ contains $n(n-k)u_{m-3}-nu_{m-4}$ vertical edges and $H_{m-2}^{(k+1)}\sqcup H_m^{(k+1)}$ contains $n(n-k)u_{m-2}-nu_{m-3}$ horizontal edges.

  Assuming $H_{m-2}^{(k+1)}\subset S_{H,k+1}$ and $S_V^{(k+1)}=V_m^{(k+1)}$, we have $S_V\cap V_{m-2}^{(k+1)}=\varnothing$ and $S_H\cap H_m^{(k+1)}=\varnothing$ by piecewise compatibility.
  Let $h\in H_m^{(k)}$ be the horizontal edge corresponding to the first horizontal edge of $H_{m-2}^{(k+1)}$.
  Then, since there are $(n-k)u_{m-3}-u_{m-4}$ horizontal edges in $H_{m-2}^{(k+1)}$, the local shadow path $D(h;S_H)$ contains $n\big((n-k)u_{m-3}-u_{m-4}\big)$ vertical edges and is thus equal to $hv_{u_{m-1}}$.
  Similarly, the local shadow path $D(v_{u_{m-1}};S_V)$ is also equal to $hv_{u_{m-1}}$.
  In particular, neither of the compatibility conditions of Definition~\ref{def:compatibility} are satisfied for the path $hv_{u_{m-1}}$ and so $(S_H,S_V)$ is not compatible.

  For the forward implication, we work by induction on $m\ge4$.
  Consider a pair $(S_H,S_V)$ for $D_4^{(k)}$ as above which is not compatible.
  Following Theorem~\ref{th:blocking edge conditions}, write $h\in H_4^{(k)}$ for the blocking edge of $S_H$.
  Then the number of vertical edges in the local shadow path $D(h;S_H)=hv_{u_3}$ must be divisible by $n$. 
  Since $(S_H^{(k+1)},S_V^{(k+1)})$ is compatible, we must have $h\in H_{3,k}$.
  But observe that $|V_m^{(k)}|=(n-k)n-1$ and so the divisibility condition above implies $h\in H_{3,k}^{(n-1)}$.
  But $S_V$ is strongly right-justified with respect to $h$ and thus the number of horizontal edges in $D(v_{u_3};S_V)=hv_{u_3}$ is divisible by $n$.
  Identifying $H_{3,k}^{(n-1)}$ with $H_2^{(1)}$, this divisibility condition only occurs when $h$ is the first horizontal edge in $H_2^{(k+1)}\subset H_2^{(1)}$.
  Then by piecewise compatibility, the vertical edge of $H_2^{(1)}$ cannot be an element of $S_V$ and we must have $V_4^{(k+1)}\subset S_V$.
  By piecewise compatibility again, this implies $H_4^{(k+1)}\cap S_H=\varnothing$ and so $D(h;S_H)=hv_{u_3}$ implies $H_2^{(k+1)}\subset S_H$.

  To continue, let $(S_H,S_V)$ be a pair for $D_m$, $m\ge5$, which is not compatible.
  Write $\varphi:H_{m-1}\to V_m$ for the bijection given by $\varphi(h_i)=v_i$ for $1\le i\le u_{m-1}$.
  For any subset $T\subset H_{m-1}$, set $\varphi^*(T)=V_m\setminus\varphi(T)$.
  Clearly, the map $\varphi^*$ gives a bijection between subsets of $H_{m-1}$ and subsets of $V_m$.
  In Section 3.2 of \cite{rupel}, a new pair of subsets $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ for $D_{m-1}$ is given, we refer the reder to \emph{loc. cit} for notation.
  By \cite[Proposition 3.10]{rupel}, the pair $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ is not compatible, but is piecewise compatible by \cite[proposition 3.16]{rupel}.
  Thus by induction, we must have $H_{m-3}^{(k+1)}\subset(\varphi^*)^{-1}S_V$ and $V_{m-1}^{(k+1)}\subset\Omega^{-1}S_H$.
  It follows from piecewise compatibility that $H_{m-1}^{(k+1)}\cap(\varphi^*)^{-1}S_V=\varnothing$.
  But then by the definition of $\varphi^*$ we have $V_{m-2}^{(k+1)}\cap S_V=\varnothing$ and $S_V^{(k+1)}=V_m^{(k+1)}$ so that $D(v_{u_{m-1}};S_V)=hv_{u_{m-1}}$ with $h$ as in the first case above.
  Since $(S_H,S_V)$ is not compatible, Theorem~\ref{th:blocking edge conditions} states that $h$ must be the blocking edge for $S_H$ and we must have $D(h;S_H)=hv_{u_{m-1}}$.
  But this can only occur if $H_{m-2}^{(k+1)}\subset S_H$ since $H_m^{(k+1)}\cap S_H=\varnothing$ by piecewise compatibility.
\end{proof}

@@

Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.

@@

\bibitem{rupel} Rupel, D.: Rank Two Non-Commutative Laurent Phenomenon and Pseudo-Positivity, arXiv.
